An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-03-31 tex/paper.tex
2 -> multiple for HS contributions.
Adding authors.
Correct affiliation for Thomas.
Correct affiliation for James.
Prob end tournaments removed.

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{minted}  % Code
\usepackage{graphicx}  % Images
\usepackage{subcaption}  % Subfigures

@@

\author{Owen Campbell\\
        \and
        Marc Harper\\
        \and
        Vincent Knight\\
        \and
        Karol Langner\\
}

@@

\maketitle

@@

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have been in terms of strategies. One strategy
is the creation of an undergraduate mathematics student with little prior
knowledge of programming. Two other strategies were written by a 15 year old
secondary school student. As well as these strategy contributions, vital
architectural improvements to the library itself have also been received. You
can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

These capabilities are constantly being updated. Some immediate further work
includes allowing for tournaments of probabilistic length as well as further
implementation of known strategies.

>>>>

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{minted}  % Code
\usepackage{graphicx}  % Images
\usepackage{subcaption}  % Subfigures
\usepackage{authblk}  % Authors

@@

% Core devs (alphabetic order of last name)
\author[1]{Owen Campbell}
\author[1]{Mark Harper}
\author[2]{Vincent Knight}
\author[1]{Karol Langner}

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl ?}

% Affiliations
\affil[1]{Not affiliated}
\affil[2]{Cardiff University}
\affil[3]{The University of Manchester}
\affil[4]{The University of Edinburgh}
\affil[5]{St. Nicholas Catholic High School, Hartford}

% Corresponding author

@@

\maketitle
\begin{center}
    \thanks{Corresponding author: Vincent Knight
        \href{mailto:knightva@cf.ac.uk}{knightva@cf.ac.uk}}
\end{center}

@@

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have been in terms of strategies. One strategy
is the creation of an undergraduate mathematics student with little prior
knowledge of programming. Multiple other strategies were written by a 15 year old
secondary school student. As well as these strategy contributions, vital
architectural improvements to the library itself have also been received. You
can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Tournaments with probabilistic ending of interactions;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

These capabilities are constantly being updated.
